A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-03 paper.tex
Add description of seed and update mam figure

\subsection{The Message Streams}
A channel/endpoint is a stream of MAM transaction bundles, which consist of signature and the masked message payload. To publish a MAM message to channel, MAM deploys MSS to sign the message payload to channel, where $channel\ ID = root$ i.e., the MSS Merkle root. Furthermore, the structure of channel/endpoint implements forward linking, each address of a message can be derived from the previous one that other entities can fetch the next payload. This design also brings the advantage of forward secrecy, where no one has access to the data back from his/her entry point. Figure.~\ref{fig:mam_structure} shows the structure of MAM channel/endpoint.

\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{mam_structure}
    \caption{A user can generate multiple channels, which can then generate multiple endpoints. The IDs of channel and endpoint are the roots of different Merkle trees in MSS. The "central endpoint" has ID, where $endpoint\ ID = channel\ ID$}
    \label{fig:mam_structure}
\end{figure}

>>>>

\subsection{The Message Streams}
A channel/endpoint is a stream of MAM transaction bundles, which consist of signature and the masked message payload. To publish a MAM message to channel, MAM deploys MSS to sign the message payload to channel, where $channel\ ID = root$ i.e., the MSS Merkle root. The Merkle tree is generated with \textbf{seed}, an identifier of its owner in the IOTA protocol, represents the ownership of all things associated with the user in the IOTA ecosystem. Furthermore, the structure of channel/endpoint implements forward linking, each address of a message can be derived from the previous one that other entities can fetch the next payload. This design also brings the advantage of forward secrecy, where no one has access to the data back from his/her entry point. Figure.~\ref{fig:mam_structure} shows the structure of MAM channel/endpoint.

\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{mam_structure}
    \caption{With a seed, users can generate multiple channels, which can then generate multiple endpoints. The IDs of channel and endpoint are the roots of different Merkle trees in MSS. The "central endpoint" are endpoints that has ID, where $endpoint\ ID = channel\ ID$.}
    \label{fig:mam_structure}
\end{figure}
